\documentclass[letterpaper,fontsize=10pt]{scrartcl}
\usepackage{tabularx}
\usepackage[none]{hyphenat}
\usepackage[utf8x]{inputenc}
\usepackage{lmodern,textcomp}
\usepackage{enumitem}
\usepackage{ltablex}
\usepackage[english]{babel}
\usepackage[paperheight=279.4mm,paperwidth=210mm,bottom=10em]{geometry}
\usepackage{microtype}
\usepackage{blindtext}
\usepackage{titlesec}
\renewcommand{\thesection}{\Roman{section}}
\titleformat{\section}
{\normalfont\bfseries}{\thesection}{0em}{}
\renewcommand{\thesubsection}{\Roman{subsection}}
\titleformat{\subsection}
{\normalfont\mdseries\itshape}{\thesubsection}{0em}{}
\setcounter{secnumdepth}{0}

\usepackage[hidelinks,bookmarks=true]{hyperref}
\hypersetup{
    unicode=false,
    pdftoolbar=true,
    pdfmenubar=true,
    pdffitwindow=false,
		pdfstartview={FitH},
    pdftitle={Anthony Kevins},
    pdfauthor={Anthony Kevins},
    pdfsubject={Academic CV},
    bookmarksopen=true,
    bookmarksopenlevel=2,
    pdfstartview=Fit,
    pdfpagemode=UseOutlines,
		pdfnewwindow=true,
		pdfborder={0 0 0}
}
\usepackage{bookmark}

\setlength\parindent{0pt}
\setlist[itemize]{leftmargin=*}
\raggedbottom

\begin{document}

	%HEADER
	\begin{minipage}[t]{0.5\textwidth}
		\huge \textbf{Anthony Kevins}\\
		\normalsize

		School of Governance\\
		Utrecht University\\
		Bijlhouwerstraat 6\\
		3511 ZC Utrecht, The Netherlands\\
	\end{minipage}
	\begin{minipage}[t]{0.5\textwidth}
		\scriptsize \textbf{October 2018}\\
		\normalsize

		Phone: +31(0)30 253 4951\\
		Email: \href{mailto:a.v.kevins@uu.nl}{a.v.kevins@uu.nl}\\
		Website: \href{https://anthonykevins.github.io/}{anthonykevins.github.io/}\\
		ORCID: \href{https://orcid.org/0000-0003-3172-6632}{0000-0003-3172-6632}\\
	\end{minipage}

	\hrulefill

	%ACADEMIC POSITIONS
	\section{Academic Positions}
	\vspace{-1.5em}
	\begin{tabularx}{\textwidth}{@{} l X @{} }
		2017- & Marie Curie Research Fellow, School of Governance, Utrecht University\\
	& \textbullet\ Individual Fellowship (Supervisor: Barbara Vis)\\[1ex]
		2014-2017 & Assistant Professor, Department of Political Science, Aarhus University\\
				& \textbullet\ Limited term appointment, affiliated with the UNIWEL research project (Supervisors: Carsten Jensen and Kees van Kersbergen)\\
	\end{tabularx}

	%EDUCATION
	\section{Education}
	\vspace{-1.5em}
	\begin{tabularx}{\textwidth}{@{} l X @{} }
		2008-2014 & PhD, Political Science, McGill University\\
		& \textbullet\ Supervisor: Stuart N. Soroka\\
		& \textbullet\ Committee Members: Antonia Maioni and Hudson Meadwell\\
		& \textbullet\ Examination Fields: Comparative Politics (Western Europe and US); IR\\[1ex]
		2006-2007 & MSc (with Merit), Comparative Politics, London School of Economics and Political Science\\[1ex]
		2002-2006 & BA (Summa Cum Laude), Political Science and Law \& Society, York University\\
	\end{tabularx}

	%RESEARCH INTERESTS
	\section{Research Interests}
	\vspace{-1.5em}
	\begin{tabularx}{\textwidth}{@{}X}
		Public Opinion, Social Welfare and Healthcare Policy, European Politics, Democratic Representation, Inequality.\\
	\end{tabularx}

	%PUBLICATIONS
	\section{Publications}

	\vspace{-.5em}
\subsection{Books (Peer-Reviewed)}
	\vspace{-1.5em}
	\begin{tabularx}{\textwidth}{@{} l X @{} }
		2017 & \textbf{Anthony Kevins}. \textit{Expanding Welfare in an Age of Austerity: Increasing Protection in an Unprotected World}, Amsterdam University Press (Series: Changing Welfare States).
	\end{tabularx}

	\vspace{-.25em}
\subsection{Journal Articles (Peer-Reviewed)}
	\vspace{-1.5em}
	\begin{tabularx}{\textwidth}{@{} l X @{} }
    \textit{n.d.} &  \textbf{Anthony Kevins} and Kees van Kersbergen. ``The Effects of Welfare State Universalism on Migrant Integration'', \textit{Policy \& Politics} (forthcoming).\\[1ex]
    2018 & Carsten Jensen and \textbf{Anthony Kevins}. ``Numbers and Attitudes Towards Welfare State Generosity'', \textit{Political Studies} (OnlineFirst). [Downloads: 219. Altmetric Score: 14. Google Scholar Citations: 0.] \href{https://doi.org/10.1177/0032321718780516}{doi.org/10.1177/0032321718780516}\\[1ex]
    2018 & \textbf{Anthony Kevins}, Alexander Horn, Carsten Jensen, and Kees van Kersbergen. ``The Illusion of Class in Welfare State Politics?'', \textit{Journal of Social Policy} (OnlineFirst). [Downloads: 82. Altmetric Score: 10. Google Scholar Citations: 0.] \href{https://dx.doi.org/10.1017/S0047279418000247}{dx.doi.org/10.1017/S0047279418000247}\\[1ex]
    2018 & \textbf{Anthony Kevins}. ``Dualized Trust: Risk, Social Trust, and the Welfare State'', \textit{Socio-Economic Review} (OnlineFirst). [Downloads: 243. Altmetric Score: 8. Google Scholar Citations: 4.] \href{https://doi.org/10.1093/ser/mwx064}{doi.org/10.1093/ser/mwx064}\\[1ex]
    2018 & \textbf{Anthony Kevins}, Alexander Horn, Carsten Jensen, and Kees van Kersbergen. ``Yardsticks of Inequality: Preferences for Redistribution in Advanced Democracies'', \textit{Journal of European Social Policy}, 28(4): 402-418. [Downloads: 260. Altmetric Score: 8. Google Scholar Citations: 1.] \href{https://doi.org/10.1177/0958928717753579}{doi.org/10.1177/0958928717753579}\\[1ex]
		2018 & Alexander Horn and \textbf{Anthony Kevins}. ``Problem Pressure and Social Policy~Innovation: Lessons from 19th-Century Germany'', \textit{Social Science History}, 42(3): 495-515. [Downloads: 33. Altmetric Score: N/A. Google Scholar Citations: 2.] \href{https://doi.org/10.1017/ssh.2018.13}{doi.org/10.1017/ssh.2018.13}\\[1ex]
		2018 & \textbf{Anthony Kevins} and Stuart Soroka. ``Growing Apart? Partisan Sorting~in Canada, 1992-2015'', \textit{Canadian Journal of Political Science}, 51(1): 103-133. [Downloads: 321. Altmetric Score: 14. Google Scholar Citations: 1.] \href{https://doi.org/10.1017/S0008423917000713}{doi.org/10.1017/S0008423917000713}\\[1ex]
		& $\circ$ Media coverage in \href{https://www.theglobeandmail.com/opinion/big-tent-politics-is-now-all-but-dead/article24944734/}{The Globe and Mail}.\\
		2017 & Alexander Horn, \textbf{Anthony Kevins}, Carsten Jensen, and Kees van Kersbergen. ``Peeping at the Corpus – What is Really Going on Behind the Equality and Welfare Items of the Manifesto Project?'', \textit{Journal of European Social Policy}, 27(5): 403-416. [Downloads: 661. Altmetric Score: 2. Google Scholar Citations: 7.] \href{https://doi.org/10.1177/0958928716688263}{doi.org/10.1177/0958928716688263}\\[1ex]
		2016 & Stuart Soroka, Richard Johnston, \textbf{Anthony Kevins}, Keith Banting, and Will Kymlicka. “Migration and Welfare State Spending'', \textit{European Political Science Review}, 8(2): 173-194. [Downloads: 567. Altmetric Score: 14. Google Scholar Citations: 22.]
		\href{https://doi.org/10.1017/S1755773915000041}{doi.org/10.1017/S1755773915000041}\\[1ex]
		2015 & \textbf{Anthony Kevins}. ``Political Actors and the Extension of Welfare Coverage'', \textit{Journal of European Social Policy}, 25(3): 303-315. [Downloads: 215. Altmetric Score: 0. Google Scholar Citations: 3.] \href{https://doi.org/10.1177/0958928715588705}{doi.org/10.1177/0958928715588705}
	\end{tabularx}

	%ONGOING PROJECTS
	\section{Ongoing Projects}
	\vspace{-.5em}

	\subsection{Under Review}
		\vspace{-.5em}
	\begin{itemize}[noitemsep]
		\item Anthony Kevins, Alexander Horn, Carsten Jensen, and Kees van Kersbergen. ``Motive Attribution and the Moral Politics of the Welfare State''. \textbf{Revise and Resubmit} at the \textit{Journal of Social Policy}.
    \item Anthony Kevins and Naomi Lightman. ``Immigrant Sentiment and Labour Market Vulnerability: Economic Perceptions of Immigration in Dualised Labour Markets''. Submitted to \textit{Comparative European Politics}.
    \item Alexander Horn, Anthony Kevins, Carsten Jensen, and Kees van Kersbergen. ``How Parties (Do Not) Appeal to Social Groups: Hollowing of Democracy or Hyper-Adaptive Targeting?''. Submitted to \textit{European Political Science Review}.
    \item Naomi Lightman and Anthony Kevins. ``Bonus or Burden?: Care Work and Job Satisfaction in Eighteen European Countries''. Submitted to \textit{European Sociological Review}.
	\end{itemize}

	\vspace{-1.5em}
\subsection{Works in Progress}
	\vspace{-.5em}
	\begin{itemize}[noitemsep]
		\item ``Who Should have a Say?: Preferences for Differentiated Representation''. Targeted Journal: \textit{Comparative Political Studies}.
    \item ``Race, Class, or Both?: Responses to Candidate Characteristics in the UK and Canada''. Targeted Journal: \textit{Political Studies}.
		\item ``Workfare and Public Opinion'', Anthony Kevins, Alexander Horn and Kees van Kersbergen. Targeted Journal: \textit{European Journal of Political Research}.
    \item ``No Party, No Problem: Inferring Partisanship from Label-less Candidate Vignettes'', Seonghui Lee and Anthony Kevins. Targeted Journal: \textit{Journal of Politics}.
  	\item ``Decomposing Public Support for the Welfare State'', Anthony Kevins and Seonghui Lee. Targeted Journal: \textit{European Journal of Political Research}.
		\item ``Race and Differentiated Representation: The Case of Police Guidelines'', Anthony Kevins and Joshua Robison. Targeted Journal: \textit{Political Behavior}.
    \item ``Causes and Consequences of Labour Market Exploitation'', Anthony Kevins and Rebecca Paraciani. Targeted Journal: \textit{Work, Employment and Society}.
	\end{itemize}

		%GRANTS AND FELLOWSHIPS
		\section{Grants and Fellowships}
		\vspace{-1.5em}
		\begin{tabularx}{\textwidth}{@{} l X @{} }
			2017-2019 & Marie Skłodowska-Curie Individual Fellowship (Grant no. 750556), €165 598. Funder: EU, Horizon 2020 Programme.\\
			2017 & Aarhus University Departmental Research Grant (co-PI with Carsten Jensen), 45000 DKK. Funder: Department of Political Science, Aarhus University.\\
			2013-2014 & McGill Institute for Health and Social Policy Research Fellowship, \$5000. Funder: McGill Institute for Health and Social Policy.\\
			2010-2013 & Guy Drummond Fellowship, \$37500. Funder: McGill University.\\
			2010 & Consortium on Qualitative Research Methods IQMR Funding. Funder: Department of Political Science, McGill University.\\
			2008-2010 & Nathan Steinberg Fellowship in Political Science, \$30000. Funder: McGill University.\\
			2008-2009 & Provost Graduate Fellowship, \$2000. Funder: McGill University.
		\end{tabularx}

	%PAPER PRESENTATIONS (LAST FIVE YEARS)
	\section{Paper Presentations (last five years)}
	\vspace{-1.5em}
	\begin{tabularx}{\textwidth}{@{} l X @{} }
    2018 & ``Who Should Have a Say?: Preferences for Differentiated Representation''. Annual Meeting of the American Political Science Association, Boston, MA.\\[1ex]
    2018 & ``Bonus or Burden? Care Work and Job Satisfaction in Eighteen European Countries'' with Naomi Lightman. Annual Conference of the American Sociological Association, Philadelphia, PA.\\[1ex]
    2018 & ``Who Should Have a Say?: Preferences for Differentiated Representation''. Annual Meeting of the Dutch and Flemish Political Science Associations, Leiden, the Netherlands.\\[1ex]
		2017 & ``Who Should Have a Say?: Preferences for Unequal Representation''. Workshop on Democratic Representation, Aarhus University, Aarhus, Denmark.\\[1ex]
		2017 & ``The Illusion of the Middle Class in Welfare State Politics'', with Alexander Horn, Carsten Jensen, and Kees van Kersbergen. 24th International Conference of Europeanists, Glasgow, UK.\\[1ex]
		2017 & ``Perceived Class Position and the Welfare State'', with Alexander Horn, Carsten Jensen, and Kees van Kersbergen. Workshop on The Middle Class and the Welfare State, Aarhus University, Aarhus, Denmark.\\[1ex]
		2016 & ``Selfish, Good-hearted, or Nasty? Motive Attribution and the Moral Economy of the Welfare State'' with Carsten Jensen and Alexander Horn. Annual Meeting of the American Political Science Association, Philadelphia, PA.\\[1ex]
		2016 & ``How Parties (Do Not) Appeal to Social Group'' with Alexander Horn, Kees van Kersbergen, and Carsten Jensen. Annual Meeting of the Danish Political Science Association, Vejle, Denmark.\\[1ex]
		2015 & ``The Special Path? Asymmetric Federalism, Problem Pressure, and the Development of the German Welfare State'', with Alexander Horn. Annual Meeting of the Danish Political Science Association, Kolding, Denmark.\\[1ex]
		2015 & ``Yardsticks of Inequality'', with Carsten Jensen, Kees van Kersbergen, and Alexander Horn. Twenty-second International Conference of Europeanists, Paris, France.\\[1ex]
		2015 & ``Inequality, Parties, and Public Opinion'' with Alexander Horn. Network for Political Studies of Inequality Workshop, University of Southern Denmark, Odense, Denmark.\\[1ex]
		2015 & ``Peeping at the Corpus: What is Really Going on Behind the Equality and Welfare Items of the Manifesto Project?'', with Alexander Horn, Kees van Kersbergen, and Carsten Jensen. Manifesto Project User Conference, Berlin, Germany.\\[1ex]
		2015 & ``Yardsticks of Inequality'', with Carsten Jensen, Kees van Kersbergen, and Alexander Horn. 27th Annual Meeting of the Society for the Advancement of Socio-Economics, London, England.\\[1ex]
		2015 & ``The Welfare State, Statecraft, and Migration: Social Policy and Integration in Denmark and Canada'', with Kees van Kersbergen, Carsten Jensen, and Alexander Horn. Annual Conference of the Canadian Political Science Association, Ottawa, Canada.\\[1ex]
		2014 & ``The Strivers and the Skivers: Public Opinion, Political Discourse, and Changes to Benefit Access''. Annual Conference of the Canadian Political Science Association, St. Catharines, Canada.\\[1ex]
		2014 & ``Redistributive Preferences and Partisan Polarization: Canada in Comparative Perspective'', with Stuart Soroka. Workshop on Canadianizing the United States? Public Opinion across the 49th Parallel, University of California, Berkeley, Berkeley, CA.\\[1ex]
		2014 & ``The Strivers and the Skivers: Public Opinion, Political Discourse, and Changes to Benefit Access''. Twenty-first International Conference of Europeanists, Washington, DC.\\[1ex]
		2013 & ``Extending and Standardising Care: Healthcare Reform in France and Italy''. Twentieth International Conference of Europeanists, Amsterdam, The Netherlands.\\[1ex]
		2013 & ``Migration and Welfare State Spending'', with Stuart Soroka, Richard Johnston, Keith Banting, and Will Kymlicka. Twentieth International Conference of Europeanists, Amsterdam, The Netherlands.\\[1ex]
		2013 & ``Migration and Welfare State Spending'', with Stuart Soroka, Richard Johnston, Keith Banting, and Will Kymlicka. Annual Conference of the Canadian Political, Victoria, Canada.\\[1ex]
		2013 & ``Political Actors and the Extension of Welfare Coverage: Benefits for the Unemployed in France and Italy''. Annual Conference of the Canadian Political, Victoria, Canada.
	\end{tabularx}

	%TEACHING
	\section{Teaching}
	\vspace{-.5em}
	\begin{itemize}[noitemsep]
			\item Co-Instructor, “Political Institutions: Western countries, The European Union and International Institutions”
			\begin{itemize}[noitemsep]
					\item Overview: Bachelor’s Core Course, Aarhus University, Spring 2016 \& 2017
					\item Duties: Course design, lectures, exam design, and weekly seminars
          \item In-Class Teaching Time: Approximately 94 hours (per semester)
          \item Enrolment: 311 \& 317
					\item Course Description: A survey course on institutionalism and various domestic and supranational institutions, with a particular focus on the EU
			\end{itemize}
			\item Co-Instructor, “Social Science Methods for Journalists”
			\begin{itemize}[noitemsep]
					\item Overview: Master’s Core Course, Aarhus University, Fall 2016
					\item Duties: Course design, lectures, exam design, grading, and weekly seminars
          \item In-Class Teaching Time: Approximately 30 hours
					\item Enrolment: 80
					\item Course Description: An introduction to social science research design and methods (both quantitative and qualitative)
			\end{itemize}
			\item Instructor, “Democracy and Representation”
			\begin{itemize}[noitemsep]
					\item Overview: Master’s Seminar, Aarhus University, Fall 2015
					\item Duties: Course design, instruction, exam design, and grading
          \item In-Class Teaching Time: Approximately 45 hours
					\item Enrolment: 11
					\item Course Description: An exploration of the bi-directional link between public opinion and policy making, including patterns of unequal representation
			\end{itemize}
			\item Instructor, “Pragmatism and Politics”
			\begin{itemize}[noitemsep]
					\item Overview: Master’s Seminar, Aarhus University, Spring 2015
					\item Duties: Course design, instruction, exam design, and grading
          \item In-Class Teaching Time: Approximately 45 hours
					\item Enrolment: 4
					\item Course Description: An examination of the challenges underlying the balance between technocracy and democracy
			\end{itemize}
			\item Instructor, “Politics: Contemporary Europe”
			\begin{itemize}[noitemsep]
					\item Overview: Bachelor’s Course, McGill University, Summer \& Fall 2013
					\item Duties: Course design, lectures, exam design, and grading
          \item In-Class Teaching Time: Approximately 38 hours (per semester)
					\item Enrolment: 34 \& 75
					\item Course Description: A survey of welfare state, capitalist, and citizenship regime typologies, as well as the policy changes across them
			\end{itemize}
	\end{itemize}

	%PROFESSIONAL TRAINING
	\vspace{-1em}
\section{Professional Training}
\vspace{-.5em}

\phantomsection
\addcontentsline{toc}{subsection}{Methodological Training} \textit{Methodological Training:} Essex Summer School in Social Science Data Analysis (2015); the Centre for the Study of Democratic Citizenship (2013-2014); the Institute for Qualitative and Multi-Method Research (2010); McGill University (2008-2010).\\[-1ex]

\phantomsection
\addcontentsline{toc}{subsection}{Pedagogical Training} \textit{Pedagogical Training:} Pedagogical Programme for Assistant Professors, Aarhus University (2016-2017); Challenges of the Multicultural Classroom in a Danish Context, Aarhus University (2016).\\[-1ex]

\phantomsection
\addcontentsline{toc}{subsection}{Language Training} \textit{Language Training:} French language course - Advanced (C1) Level, Alliance Française (2018-); Certificate of Proficiency in Written French – Workplace Communication, McGill University (2017); Danish language courses, Lærdansk (2014-2016); Explore - French Immersion Program (La Pocatière, Québec), Campus Saint-Jean, University of Alberta (2010).\\[-1ex]

\phantomsection
\addcontentsline{toc}{subsection}{Software Competencies} \textit{Software Competencies:} Stata; R; Git; Qualtrics; \LaTeX ; Markdown.

	%PROFESSIONAL SERVICE
\section{Professional Service}

	\vspace{-.5em}
	\subsection{Professional Affiliations}
	\vspace{-.5em}
		\begin{itemize}[noitemsep]
		\item Political Institutions, Behaviour and Decision Making Workshop (2017-)
		\item Network for Political Studies of Inequality (2015-2017)
		\item Universalism and the Welfare State Research Group, Aarhus University (2014-2017)
		\item Research Fellow, McGill Institute for Health and Social Policy (2013-2014)
		\item Student Member, Centre for the Study of Democratic Citizenship (2013-2014)
		\item Short-term Visitor, European University Institute (2013)
	\end{itemize}

	\phantomsection
	\addcontentsline{toc}{subsection}{Community Engagement} \textit{Community Engagement}: Research outreach via the \href{http://blogs.lse.ac.uk/politicsandpolicy/how-claims-about-welfare-benefit-levels-affect-public-opinion/}{LSE British Politics \& Policy Blog} (2018); Invited talk at the Department of Health and Care, Aarhus Municipality, Denmark (2015).\\ [-1ex]

	\phantomsection
	\addcontentsline{toc}{subsection}{Association Memberships} \textit{Association Memberships}: American Political Science Association; Dutch Political Science Association.\\ [-1ex]

	\phantomsection
	\addcontentsline{toc}{subsection}{Panel Discussant} \textit{Panel Discussant}:	Conference of Europeanists (2017); Annual Meeting of the Danish Political Science Association (2015).\\ [-1ex]

	\phantomsection
	\addcontentsline{toc}{subsection}{Reviewer} \textit{Reviewer}: Journal of European Social Policy; Journal of Politics; Journal of Public Policy; Policy Sciences; Social Policy \& Administration; Socio-Economic Review.

	%LANGUAGES
	\section{Languages}
	\vspace{-.25em}
	\begin{itemize}[noitemsep]
		\item English: Native
		\item French: Advanced (C1)
		\item Italian: Upper intermediate (B2)
		\item Danish: Intermediate (B1)\\ [-1.5ex]
	\end{itemize}

	%CITIZENSHIP
\phantomsection
	\addcontentsline{toc}{section}{Citizenship} \textbf{Citizenship}: Canadian

	%REFERENCES
\section{References}
		\vspace{-.5em}

	\begin{minipage}[t]{0.54\textwidth}
		Carsten Jensen, Professor\\
		Department of Political Science\\
		Aarhus University\\
		Bartholins Allé 7, Building 1340, Rm 227\\
		8000 Aarhus C, Denmark\\
		Tel.: +45 87165678\\
		Email: carstenj@ps.au.dk\\
	\end{minipage}
	\begin{minipage}[t]{0.46\textwidth}
		Kees van Kersbergen, Professor\\
		Department of Political Science\\
		Aarhus University\\
		Bartholins Allé 7, Building 1340, Rm 229\\
		8000 Aarhus C, Denmark\\
		Tel.: +45 87165727\\
		Email: kvk@ps.au.dk\\
	\end{minipage}
	\smallskip

	\begin{minipage}[t]{0.54\textwidth}
	Stuart Soroka, Professor\\
	Communication Studies \& Political Science\\
	University of Michigan\\
	Room 4448, 426 Thompson Street\\
	Ann Arbor, MI 48104–2321\\
	Tel.: +1 734 764 8362\\
	Email: ssoroka@umich.edu\\
\end{minipage}
\begin{minipage}[t]{0.46\textwidth}
	Barbara Vis, Professor\\
	School of Governance\\
	Utrecht University\\
	Bijlhouwerstraat 6\\
	3511 ZC Utrecht, The Netherlands\\
	Tel.: +31(0)30 253 4935\\
	Email: b.vis@uu.nl
\end{minipage}

\end{document}
