\documentclass[letterpaper,fontsize=10pt]{scrartcl}
\usepackage{tabularx}
\usepackage[none]{hyphenat}
\usepackage[utf8x]{inputenc}
\usepackage{lmodern,textcomp}
\usepackage{enumitem}
\usepackage{ltablex}
\usepackage[english]{babel}
\usepackage[paperheight=279.4mm,paperwidth=210mm,bottom=10em]{geometry}
\usepackage{microtype}
\usepackage{blindtext}
\usepackage{titlesec}
\renewcommand{\thesection}{\Roman{section}}
\titleformat{\section}
{\normalfont\bfseries}{\thesection}{0em}{}
\renewcommand{\thesubsection}{\Roman{subsection}}
\titleformat{\subsection}
{\normalfont\mdseries\itshape}{\thesubsection}{0em}{}
\setcounter{secnumdepth}{0}

\usepackage[hidelinks,bookmarks=true]{hyperref}
\hypersetup{
    unicode=false,
    pdftoolbar=true,
    pdfmenubar=true,
    pdffitwindow=false,
		pdfstartview={FitH},
    pdftitle={Anthony Kevins},
    pdfauthor={Anthony Kevins},
    pdfsubject={Publications},
    bookmarksopen=true,
    bookmarksopenlevel=2,
    pdfstartview=Fit,
    pdfpagemode=UseOutlines,
		pdfnewwindow=true,
		pdfborder={0 0 0}
}
\usepackage{bookmark}

\setlength\parindent{0pt}
\setlist[itemize]{leftmargin=*}
\raggedbottom

\usepackage{fancyhdr}
\setlength{\parskip}{1em}

\pagestyle{fancy}
\fancyhf{}
\fancyhead[LE,RO]{Anthony Kevins}
\fancyhead[RE,LO]{Publication List}
\fancyfoot[CE,CO]{\leftmark}
\fancyfoot[LE,CO]{\thepage}
\setlength\parindent{0pt}
\setlist[itemize]{leftmargin=*}

\setenumerate[1]{label={[\arabic*]}}

\newenvironment{modenumerate}
  {\enumerate\setupmodenumerate}
  {\endenumerate}

\newif\ifmoditem
\newcommand{\setupmodenumerate}{%
  \global\moditemfalse
  \let\origmakelabel\makelabel
  \def\moditem##1{\global\moditemtrue\def\mesymbol{##1}\item}%
  \def\makelabel##1{%
    \origmakelabel{##1\ifmoditem\rlap{\mesymbol}\fi\enspace}%
    \global\moditemfalse}%
}

\begin{document}

\sloppy

Below you will find a list of my published research. Publications marked with an asterisk are included with my application, and the co-authored writing samples are accompanied by a corresponding co-authorship statement that specifies my contribution to the article.

\section{Books (Peer-Reviewed)}
\vspace{-1.5em}
\begin{modenumerate}
	\moditem{*}	Kevins, Anthony. (2017) \textit{Expanding Welfare in an Age of Austerity: Increasing Protection in an Unprotected World}, Amsterdam University Press (Series: Changing Welfare States).
\end{modenumerate}

\vspace{-.25em}
\section{Journal Articles (Peer-Reviewed)}
	\vspace{-1.5em}
	\begin{modenumerate}
 			\moditem{*}	Kevins, Anthony, and Kees van Kersbergen. (Forthcoming) ``The Effects of Welfare State Universalism on Migrant Integration'', \textit{Policy \& Politics}.
			\moditem{*}	Jensen, Carsten, and Anthony Kevins. (2018) ``Numbers and Outrage in Welfare State Politics'', OnlineFirst in \textit{Political Studies}.
			\item	Kevins, Anthony, Alexander Horn, Carsten Jensen, and Kees van Kersbergen. (2018) ``The Illusion of the Class in Welfare State Politics?'', OnlineFirst in the \textit{Journal of Social Policy}.
			\moditem{*} Kevins, Anthony. (2018) ``Dualized Trust: Risk, Social Trust, and the Welfare State'', OnlineFirst in \textit{Socio-Economic Review}.
			\moditem{*}	Kevins, Anthony, Alexander Horn, Carsten Jensen, and Kees van Kersbergen. (2018) ``Yardsticks of Inequality: Median Voter Preferences for Redistribution in Advanced Democracies'', \textit{Journal of European Social Policy}, 28(4): 402-418.
			\item Horn, Alexander, and Anthony Kevins. (2018) ``Problem Pressure and Social Policy Innovation: Lessons from 19th-Century Germany'', \textit{Social Science History}, 42(3): 495-515.
      \moditem{*} Kevins, Anthony, and Stuart N. Soroka. (2018) ``Growing Apart? Partisan Sorting in Canada, 1992-2015'', \textit{Canadian Journal of Political Science}, 51(1): 103-133.
			\item Horn, Alexander, Anthony Kevins, Carsten Jensen, and Kees van Kersbergen. (2017) ``Peeping at the Corpus: What is Really Going on Behind the Equality and Welfare Items of the Manifesto Project'', \textit{Journal of European Social Policy}, 27(5): 403-416.
			\item Soroka, Stuart N., Richard Johnston, Anthony Kevins, Keith Banting, and Will Kymlicka. (2016) ``Migration and Welfare State Spending'', \textit{European Political Science Review}, 8(2), 174-193.
			\item Kevins, Anthony. (2015) ``Political Actors, Public Opinion, and the Extension of Welfare Coverage'', \textit{Journal of European Social Policy}, 25(3), 303-315.
	\end{modenumerate}

\end{document}
